---
title: "R Project Euler Solutions"
author: "Stephen Chu"
date: "Augest 6, 2017"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These are my solutions using R to the problems located at [Project Euler](https://projecteuler.net/).

## Problem 0001 - Multiples of 3 and 5
If we list all the natural numbers below 10 that are multiples of 3 or 5, we get 3, 5, 6 and 9. The sum of these multiples is 23. Find the sum of all the multiples of 3 or 5 below 1000.

```{r p0001}
result <- 0
for (i in 1:999){
  if ((i %% 3 == 0) | (i %% 5 == 0)) {
    result <- result + i
  }
}
print(result)
```

## Problem 0002 - Even Fibonacci Numbers
Each new term in the Fibonacci sequence is generated by adding the previous two terms. By starting with 1 and 2, the first 10 terms will be:

1, 2, 3, 5, 8, 13, 21, 34, 55, 89, ...

By considering the terms in the Fibonacci sequence whose values do not exceed four million, find the sum of the even-valued terms.
```{r p0002}
max_num <- 4000000
sum <- 0
a <- 0
b <- 1

while (b < max_num) {
  temp <- a
  a <- b
  b <- temp + b
  if (a %% 2 == 0) {
    sum <- sum + a
  }
}

print(sum)
```

## Problem 0003 - Largest Prime Factor
The prime factors of 13195 are 5, 7, 13 and 29. What is the largest prime factor of the number 600851475143?
```{r p0003}
prime <- 600851475143
a <- 0
x <- 1

while (x <= prime) {
  if (prime %% x == 0) {
    a <- x
    prime <- prime / x
  }
  x <- x + 1
}

print(a)
```
## Problem 0004 - Largest Palindrome Product
A palindromic number reads the same both ways. The largest palindrome made from the product of two 2-digit numbers is `9009 = 91 × 99`. Find the largest palindrome made from the product of two 3-digit numbers.
```{r}
isPalindrome <- function(num){
  if (num == '') {
    return(TRUE)
  } else if (substr(num, 1, 1) == substr(num, nchar(num), nchar(num))) {
    return(isPalindrome(substr(num, 2, nchar(num) - 1)))
  } else {
    return(FALSE)
  }
}

num <- 0
a <- 999
b <- 999
while (a > 100) {
  while (b > 100) {
    if (isPalindrome(toString(a * b))) {
      if ((a * b) >= num) {
        num = a * b
      } else {
        break
      }
    }
    b <- b - 1
  }
  a <- a - 1
  b <- 999
}
print(num)
```

